%%%% ijcai16.tex

\typeout{IJCAI-16 Instructions for Authors}

% These are the instructions for authors for IJCAI-16.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}

% Use the postscript times font!
\usepackage{times}
\usepackage[lined, boxed, linesnumbered]{algorithm2e}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{float}
\usepackage{mathtools}
\usepackage{graphicx}
% \usepackage{multicol}
\usepackage{blindtext}

\setlength{\parindent}{0pt}

\SetAlCapSkip{0.01em}


% \addtolength{\topskip}{-0.5mm}
% \addtolength{\parskip}{-0.5mm}

% \addtolength{\abovecaptionskip}{-4mm}
% \addtolength{\belowcaptionskip}{-3mm}


\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

% the following package is optional:
%\usepackage{latexsym}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

\title{Time Resource Networks}
% \author{Subbarao Kambhampati \\
% Arizona State University, Tempe Arizona  \\
% ijcai16programchair@gmail.com}

% \author{Szymon Sidor  \and Peng Yu  \and Cheng Fang \and Brian Williams\\
% Computer Science \& Artificial Intelligence Lab, MIT, Cambridge, MA\\
% \texttt{\{sidor,yupeng,cfang,williams\}@mit.edu}}
\author{Paper 487}

\begin{document}

\maketitle

\begin{abstract}
  The problem of scheduling under resource constraints is widely applicable. One prominent example is power management, in which we have a limited continuous supply of power but must schedule a number of power-consuming tasks. Such problems feature tightly coupled continuous resource constraints and continuous temporal constraints.

  We address such problems by introducing the Time Resource Network (TRN), an encoding for resource-constrained scheduling problems. The definition allows temporal specifications using a general family of representations derived from the Simple Temporal network, including the Simple Temporal Network with Uncertainty, and the probabilistic Simple Temporal Network (Fang et al. (2014)).

  We propose two algorithms for determining the consistency of a TRN: one based on Mixed Integer Programing and the other one based on Constraint Programming, which we evaluate on scheduling problems with Simple Temporal Constraints and Probabilistic Temporal Constraints.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RELATED WORK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{related}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROBLEM STATEMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{problem_statement}

%\subsection{Common scheduling problems expressed as Time Resource Network}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALGORITHM %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{approach}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FUTURE WORK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Future Work}
% \textbf{linear resource constraint} is a triplet $(x, y, r_b, r_e)$, where $x, y \in \texttt{nodes(ATN)}$ and resource usage at time $s(x) \leq t \leq s(y)$ is equal to
% \[
%     u(t) = r_b + t  \frac{r_e - r_b}{s(y) - s(x)}
% \]
% Intuitively, simple resource constraint encodes the fact that between time $s(x)$ and $s(y)$  resource is consumed/generated with rate that changes linearly between $s(x)$ and $s(y)$.
%
% \textbf{probabilistic simple resource constraint}
% Is an extension of simple resource constraint where $r$ is a random variable (and therefore so is $u(t)$).




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
In this paper, we  introduced Time Resource Networks, a general model for continuous resource-constrained continuous time scheduling problems. The definition allows flexibility in modeling our temporal constraints. We introduced two algorithms  for determining time-resource consistency of a TRN: a standard MILP-encoding based algorithm and a novel CP algorithm. We  demonstrated through computational experiments that the novel algorithm is significantly faster for networks with large number of temporal constraints and small number of resource constraints. In addition, we demonstrated that CP algorithm is flexible and can support recently introduced probabilistic simple temporal networks \cite{Fang2014}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{named}
\bibliography{ijcai16}

\end{document}
